To my parents, Michael and Karin, thank you for encouraging (and suffering through) a unceasing curiosity about how things work,
    and for providing me with a proverbial springboard of opportunities growing up.
To my brother, David, thank you for showing me that computers are indeed interesting tools,
    and for introducing me to the concepts of security and privacy at an early age
    by insisting I communicate with you via PGP when I was seven.
As a result of those efforts, no prying eyes will ever know what secrets and sensitive information we were privy to at that age...
    at least for several minutes, until they guess my passphrase ``\texttt{mA4Tn}''.

There have been many teachers and professors over the years who have been instrumental in getting me to where I am today.
I am sincerely grateful to two in particular, who have both had a profound impact on who I am:
    John Barry Smith, teacher of Mathematics at the International School of Geneva,
        who instilled within me a love of learning and a general refusal to accept mediocrity from myself;
    Philip Mulry, professor of Computer Science at Colgate University,
        whose unending enthusiasm made even the dryest of topics captivating.

Special thanks to professors Jaime Spacco and Vijay Ramachandran at Colgate University,
    and professors Vitaly Shmatikov and Lorenzo Alvisi at the University of Texas at Austin.
You lit (and more importantly, stoked and maintained) the fire of interest I felt towards higher learning.
You showed me that research was interesting, and helped me find my direction.
I wouldn't be where I am today were it not for your contributions.

A heartfelt thanks to my friends:
    Richard McPherson, for always being there when I needed a sounding-board, a voice of reason, a companion, or anything else;
    Megan Merner, for her constant love and support, and for endlessly reading and proof-reading this document.

Finally, to my advisor, Mohamed Gouda, thank you for your unending patience, guidance, and support.
Your encouragement and resolve were invaluable when setbacks and discouragement loomed.
Your skillful approach to expression and writing have been extremely helpful.
You saw me through to the completion of this endeavor, and for that I am extremely grateful.
